Model for Porous Silicon Structures with a Lateral Gradient

### 2020-11-07 paper.tex
coloque las observaciones de la Dra Vivechana y cambios bib

A variety of optical devices and applications may be based on layered
systems which have a lateral gradient in both their refractive indices
and their thicknesses. They may be fabricated of porous silicon (PS) through an
electrochemical process in which the etching current depends on position. Thus, the possibility of
predicting the local current density $j$ and the corresponding
porosity $p$ and etching rate $v$ would be desirable for a systematic design of these
structures. In this work, we propose a
simple model for the calculation of $j$
as a function of position within an electrochemical cell. We prepared
some graded single layer PS samples, measured their optical properties through
ultraviolet-visible-near infrared reflectance
spectroscopy, \notaL{Should we mention microscopy?}, and related them
to their local porosity and thickness which, together with our model, were then used to obtain
the $p$ vs. $j$ and $v$ vs. $j$ calibration curves. We corroborated
our model by comparing the calibration curves for different samples. Thus, from
measurements on only one, or a few simple systems, we may obtain full
calibration curves which may be used to predict, design, and fabricate
more complex novel nonhomogenous devices with lateral gradients which can be used
for manifold applications.

@@

\section{Introduction}
\label{sec:introduction}
Surfaces with a gradient in the refractive index (GRIN) are of
importance as they allow the engineering and tuning of the optical
phase along their surface, yielding applications such as flat
lenses. Furtheremore, there are important biological applications
which combine topographical features with index of refraction
gradients \cite{pierscionek2012gradient}. Preparation of structures
with gradients in other properties have also shown their
usefulness. \notaL{I believe the examples below are unrelated to GRIN,
  thats why I added the previous remark.} As an example, the
roughness dependent  response of cells has been tested on
materials used applications in medical implants
\cite{bai2020bioinspired}.
Gradients have also been employed for several
technological applications such as high-yield screening of catalysts,
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction,
potyrailo2008combinatorial}
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227],
synthesis of  Ag-Au alloy gradients on steel and chemical composition
gradients of CdS layers
on gold electrodes have been obtained made by Shannon’s
group\cite{wang2019fabrication}. \notaL{Is this Shannon a big shot, or
  why should we name him?}
Among electrochemical methods, compositional and doping density changes
in  conducting polymers have been used to produce gradients using Indium Tin
Oxide electrodes \cite{inagi2010bipolar}
Electrochemically induced potential gradients have been shown to catalyze the
reactions and gradient doping of polymers \cite{qin2020bipolar, ishiguro2011gradient}.
As compared to the above mentioned techniques, a relatively economical,
fast and easy approach for the fabrication
of gradient materials has been the use  of asymmetrical
electrode configurations in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.
This technique has the additional advantage of being compatible
with VLSI devices and integrable with microelectronics.

Although porous silicon (PS) initially stimulated the interest of the scientific
community due to its photoluminiscence in the visible range at room
temperature, it has presently
been recognized as a multifaceted optical material due to its large surface
area, biocompatibility, ease of fabrication and tunable refractive index.
Applications based on porous silicon now cover various fields such as
chemical sensors and biosensors \cite{kumar2020porous},
microelectronics and MEMS \cite{martinez2016dual},as well as a
range of optical \cite{estevez2014porous} and optoelectronic applications
\cite{ramadan2020fabrication}. Specifically,
the temporal variation of the current density results in a variation of
porosity along the depth, allowing the easy fabrication of different kinds
\cite{perez2018reflectivity} of 1D photonics crystals and other
structures. \notaL{Photonic crystals only in the periodic case.}
Although the conventional fabrication of PS yields laterally
homogeneous samples, with invariant structural and optical properties
along the surface, an asymmetric configuration \notaL{Is it clear what
  is asymmetric?} may produce porous
Silicon structures with a lateral gradient in properties such as
thickness, pore size and density, and thus, refractive index and
optical thickness. In this configuration, a small platinum electrode (cathode)
is positioned perpendicular  to the surface of a Si substrate (anode)
near one end \notaL{ At the center wouldn't be asymmetric: or the
  center} of the cell, resulting  in a current
density  which decreases as the distance to the electrode increases
 \cite{khung2008using, clements2011mesenchymal}.
The resulting porous surface can have pore sizes ranging from a few nanometers
to  few micrometers  \cite{wang2015screening}. The range of the dimensions of the pores and
the corresponding  thickness range on the same chip can be controlled by
adjusting the location of the electrode, the  anodizing current
and the etching time. Different
applications have been found for the resulting structures
\cite{collins2002determining}. For example, Sailor's group
\cite{collins2002determining, sailor2012porous} applied it
for the determination of protein size.
Additionally, gating of
the optical response through a variation in pH of the solution was shown to
trap/release biomolecules for possible drug delivery
applications, given the biocompatible nature of PS, . \notaL{How is this related to the gradient?}
A similar asymmetric electrode configuration was used to fabricate
multilayered optical filters with lateral a gradient
\cite{li2005painting} and
for developing ethanol sensors \cite{sailor2012porous}.
Additionally it has been shown that the combination of thermal  oxidation  and
infiltration of TiO2  by ALD \notaL{What is this acronym?} allows the manufacture
of transparent GRIN
optical elements with a high refractive index contrast \cite{ocier2017tunable}.
Kruger et al. \cite{krueger2018electrochemical} used
a porous silicon 1D GRIN structure infiltrated with polymer to
synthesize flat microlens arrays.
Recently, J Wang et al. has shown the fabrication of
a miniature spectrometer with PS based rugate filter using a
radial interfacial potential distribution \cite{wang2019fabrication}
On the other hand, the effect of different topographical
features present on the same chip, has also been
used to study the dependence of the adhesion of certain cells on the
surface topography \cite{khung2008using}.

For applications such as those mentioned above,
it would be very useful to be able to predict beforehand the spatially dependent
properties of the resulting structures. This would allow the design
and optimization of the desired devices.
In this work, we report a simple analytical model to quantitatively
analyze the spatial dependence of the current density during the
electrochemical on Si to produce PS structures. A calibration
procedure may then relate the current density to the porosity and the
etching rate. Thus, for a given etching current acting over a given
time, we may predict the position dependence of the index of
refraction and optical thickness of the resulting inhomogeneous
layer, thus allowing the prediction of the optical properties of
multilayered GRIN structure. The structure of the paper is the
following.
\notaL{Check when finished}. In Section \ref{sec:theory} we develop a
simple analytical model to calculate
the current density at any point over the GRIN structure under preparaton.
In Section \ref{sec:procedures} we provide experimental details for the
synthesis of porous silicon samples with lateral refractive index gradient.
Section \ref{sec:discussion-results} includes experimental results and
its comparison with numerically evaluated parameters. Finally, we
devote Section \ref{sec:conclusions} to our concusions.

\section{Theory}
\label{sec:theory}
\label{sec:calc-curr-dens}
\notaL{check where acronyms are first defined}
A gradient in the optical properties of porous Silicon (PS) systems may be
obtained by electrochemically attacking a Si surface with a position dependent current
density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
the current density, as well as the etching rate and the thickness of the
porous layer. Nevertheless, it is challeging to measure the
{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
design and optimization of well characterized reproducible GRIN PS
structures.\notaL{Tenemos referencias para afirmar esto?} Thus, we
believe a
system for which the current density field may be
easily computed would be useful.
Though $\bm j(\bm r)$ may be numerically calculated for any
given arbitrary experimental setup,  here we propose a particularly
simple setup that allows an expression for the current in terms
of a series that is rapidly convergent and each of whose terms is a
simple analytic function. With this setup it is easy to characterize
the dependence of different properties of interest on the current, and
this allows the design and optimization of diverse GRIN PS devices.

@@

The electrostatic potential produced by an infinite array of
charges expressed as a sum in real space of Coulomb terms has ill
convergence properties. The potential can be obtained
using the Ewald summation technique
\cite{ewald1921calculation, belhadj1991molecular-dynamics,
  schmidt1997multipole, grzybowski2000ewald, toukmaji2000efficient,
  brodka2004ewald, campione2012ewald}, which yields
two rapidly converging series, one in real space and another one in reciprocal space.
Nevertheless, as we need the potential and the field to obtain the
current density on the surface of the sample on which  no
real nor image charges lie, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors \cite{nijboer1957calculation, nijboer1958internal,
  de_wette1965internal, watson1981madelung, grindlay1981k}
\notaL{¿De qué se trata esta referencia que pusiste
  aquí: \cite{kratzer2019basics}?}, then sum over the charges that form the basis
of the 2D {\em crystal} plane, and finally sum over all the
 planes.

@@

In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture GRIN PS structures.
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a brass plate\notaC{ laton.}\notaL{Porqué
  vivechna dice silver/copper? De qué era: latón, plata, cobre, una
  aleación de cobre y plata? Era un alambre o una placa?}
which together make the anode. The
cathode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the thickness, density and depth
of the resulting pores.

@@

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra at different positions over our
samples using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer in its data collection absolute
reflectance mode, using a rectangular spot size of
$0.7\text{mm}\times2.0\text{mm}$, a slit width of $0.6\text{mm}$ and
a wavelength range from $1400\text{nm}$ to
$300\text{nm}$.\notaL{Vivechna: puedes checar si así se reportan estos parámetros?}

For interpretation of the data we used
the standard formula \cite{stenzel2015physics} for the reflectance of
a three media system:
an air environment  (0), the PS film (1) and the c-Si substrate (2),
\begin{equation}\label{Eq:ECMR}
  R=\left |\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\psi}}{1+r _ {_
        {01}}r _ {_ {12}} e^{2i\psi}}\right |^2
\end{equation}
where $r_{01}$ and $r_{12}$ are the Fresnel reflectance
coefficients of the air/PS and PS/c-Si interfaces \cite{sattler2017silicon}
and $\psi=k_1^\perp d$, where $k_1^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$. The reflectance depends on the
thickness of the film and on the index of refraction $n_1=n_{\text{PS}}$ of the porous
layer, which we relate to the porosity through Bruggeman's
effective medium theory \cite{theiss1997optical},
\begin{equation}\label{Eq:Brugg}
 p\frac{1-\epsilon_1} {1+\epsilon_1} + (1-p)
  \frac{\epsilon_2 - \epsilon_1}
  {\epsilon_2+\epsilon_1}=0,
\end{equation}
where $\epsilon_2=\epsilon_{\text{Si}}$ is the dielectric function of
the c-Si substrate, and
$\epsilon_1=n_{\text{PS}}^2$ is the dielectric function of the PS layer.
We fitted the reflectance spectra using the porosity $p$ and the
thickness $d$ and a scale calibration factor $s$ as fitting
parameters, and thus, we obtained the porosity
$p$ and the etching rate $v=d/t$ for different values of the local
current density $j_\perp$ expected at several positions on different
samples.

@@

\section*{Acknowledgments}
\label{sec:acknowledgments}
WLM acknowledges the support of DGAPA-UNAM under grant
IN111119. \notaL{Cristian debe agradecer a conacyt y faltan
  agradecimientos de Vivechna (quizás incluyendo al icf)}
\bibliographystyle{unsrt}
\bibliography{bibligrin} %Aquí ponen el nombre del archivo .bib
\end{document}

>>>>

A variety of optical devices and applications may be based on layered
systems which have a lateral gradient in both their refractive indices
and their thicknesses. They may be fabricated of porous silicon (PS) through an
electrochemical process in which the etching current depends on position. Thus, the possibility of
predicting the local current density $j$ and the corresponding
porosity $p$ and etching rate $v$ would be desirable for a systematic design of these
structures. In this work, we propose a
simple model for the calculation of $j$
as a function of position within an electrochemical cell. We prepared
some graded single layer PS samples, measured their optical properties through
ultraviolet-visible-near infrared reflectance
spectroscopy, \notaL{Should we mention microscopy?}, and related them
to their local porosity and thickness which, together with our model, were then used to obtain
the $p$ vs. $j$ and $v$ vs. $j$ calibration curves. 
\notaV{Thickness was additionally viewed through scanning electron microscopy}. We corroborated
our model by comparing the calibration curves for different samples. Thus, from
measurements on only one, or a few simple systems, we may obtain full
calibration curves which may be used to predict, design, and fabricate
more complex novel nonhomogenous devices with lateral gradients which can be used
for manifold applications.

@@

\section{Introduction}
\label{sec:introduction}
Surfaces with a gradient in the refractive index (GRIN) are of
importance as they allow the engineering and tuning of the optical
phase along their surface, yielding applications such as flat
lenses. Furtheremore, there are important biological applications
which combine topographical features with index of refraction
gradients \cite{pierscionek2012gradient}. Preparation of structures
with gradients in other properties have also shown their
usefulness. \notaL{I believe the examples below are unrelated to GRIN,
  thats why I added the previous remark.} \notaV{Response : 
ALL the examples are related to GRIN} As an example, the
roughness dependent  response of cells has been tested on
materials used applications in medical implants
\cite{bai2020bioinspired}.
Gradients have also been employed for several
technological applications such as high-yield screening of catalysts,
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction,
potyrailo2008combinatorial}
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227],
synthesis of  Ag-Au alloy gradients on steel and chemical composition
gradients of CdS layers
on gold electrodes have been obtained made by Shannon’s
group\cite{wang2019fabrication}. \notaL{Is this Shannon a big shot, or
  why should we name him?} \notaV{R : Eliminated the name}
Among electrochemical methods, compositional and doping density changes
in  conducting polymers have been used to produce gradients using Indium Tin
Oxide electrodes \cite{inagi2010bipolar}
Electrochemically induced potential gradients have been shown to catalyze the
reactions and gradient doping of polymers \cite{qin2020bipolar, ishiguro2011gradient}.
As compared to the above mentioned techniques, a relatively economical,
fast and easy approach for the fabrication
of gradient materials has been the use  of asymmetrical
electrode configurations in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.
This technique has the additional advantage of being compatible
with VLSI devices and integrable with microelectronics.

Although porous silicon (PS) initially stimulated the interest of the scientific
community due to its photoluminiscence in the visible range at room
temperature, it has presently
been recognized as a multifaceted optical material due to its large surface
area, biocompatibility, ease of fabrication and tunable refractive index.
Applications based on porous silicon now cover various fields such as
chemical sensors and biosensors \cite{kumar2020porous},
microelectronics and MEMS \cite{martinez2016dual},as well as a
range of optical \cite{estevez2014porous} and optoelectronic applications
\cite{ramadan2020fabrication}. Specifically,
the temporal variation of the current density results in a variation of
porosity along the depth, allowing the easy fabrication of different kinds
\cite{perez2018reflectivity} of 1D photonics crystals and other
structures. \notaL{Photonic crystals only in the periodic case.}
Although the conventional fabrication of PS yields laterally
homogeneous samples, with invariant structural and optical properties
along the surface, an asymmetric configuration \notaL{Is it clear what
  is asymmetric?} may produce porous
Silicon structures with a lateral gradient in properties such as
thickness, pore size and density, and thus, refractive index and
optical thickness. In this configuration, a small platinum electrode (cathode)
is positioned perpendicular  to the surface of a Si substrate (anode)
near one end \notaL{ At the center wouldn't be asymmetric: or the
  center} of the cell, resulting  in a current
density  which decreases as the distance to the electrode increases
 \cite{khung2008using, clements2011mesenchymal}.
The resulting porous surface can have pore sizes ranging from a few nanometers
to  few micrometers  \cite{wang2015screening}. The range of the dimensions of the pores and
the corresponding  thickness range on the same chip can be controlled by
adjusting the location of the electrode, the  anodizing current
and the etching time. Different
applications have been found for the resulting structures
\cite{collins2002determining}. For example, Sailor's group
\cite{collins2002determining, sailor2012porous} applied it
for the determination of protein size.
Additionally, gating of
the optical response through a variation in pH of the solution was shown to
trap/release biomolecules for possible drug delivery
applications, given the biocompatible nature of PS, . \notaL{How is this related to the gradient?}
\notaV{ The idea
here was to mention the usefulness of GRIN in portion 
size determination followed by its delivery through the variation of pH ; 
If you find this comment too way off, further applicability of protein 
size determination in drug delivery application can
 be removed "ADDITIONALLY.....applications" }
A similar asymmetric electrode configuration was used to fabricate
multilayered optical filters with lateral a gradient
\cite{li2005painting} and
for developing ethanol sensors \cite{sailor2012porous}.
Additionally it has been shown that the combination of thermal  oxidation  and
infiltration of TiO2  by \notaV{Atomic Layer Deposition} (ALD) \notaL{What is this acronym?} 
allows the manufacture
of transparent GRIN
optical elements with a high refractive index contrast \cite{ocier2017tunable}.
Kruger et al. \cite{krueger2018electrochemical} used
a porous silicon 1D GRIN structure infiltrated with polymer to
synthesize flat microlens arrays.
Recently, J Wang et al. has shown the fabrication of
a miniature spectrometer with PS based rugate filter using a
radial interfacial potential distribution \cite{wang2019fabrication}
On the other hand, the effect of different topographical
features present on the same chip, has also been
used to study the dependence of the adhesion of certain cells on the
surface topography \cite{khung2008using}.

For applications such as those mentioned above,
it would be very useful to be able to predict beforehand the spatially dependent
properties of the resulting structures. This would allow the design
and optimization of the desired devices.
In this work, we report a simple analytical model to quantitatively
analyze the spatial dependence of the current density during the
electrochemical on Si to produce PS structures. A calibration
procedure may then relate the current density to the porosity and the
etching rate. Thus, for a given etching current acting over a given
time, we may predict the position dependence of the index of
refraction and optical thickness of the resulting inhomogeneous
layer, thus allowing the prediction of the optical properties of
multilayered GRIN structure. The structure of the paper is the
following.
\notaL{Check when finished}. In Section \ref{sec:theory} we develop a
simple analytical model to calculate
the current density at any point over the GRIN structure under preparation.
In Section \ref{sec:procedures} we provide experimental details for the
synthesis of porous silicon samples with lateral refractive index gradient.
Section \ref{sec:discussion-results} includes experimental results and
it's comparison with numerically evaluated parameters. Finally, we
devote Section \ref{sec:conclusions} to our conclusions.

\section{Theory}
\label{sec:theory}
\label{sec:calc-curr-dens}
\notaL{check where acronyms are first defined}
A gradient in the optical properties of porous Silicon (PS) systems may be
obtained by electrochemically attacking a Si surface with a position dependent current
density ${\bm j(\bm r)}$, as the porosity and refractive index depend on
the current density, as well as the etching rate and the thickness of the
porous layer. Nevertheless, it is challeging to measure the
{\em local} value of $\bm j(\bm r)$ along the surface. This hampers the
design and optimization of well characterized reproducible GRIN PS
structures.\notaL{Tenemos referencias para afirmar esto?}
\notaV{NOT THAT I KNOW, so I changed the expression has been changed}
 Thus, we believe a
system for which the current density field may be
easily computed would be useful.
Though $\bm j(\bm r)$ may be numerically calculated for any
given arbitrary experimental setup,  here we propose a particularly
simple setup that allows an expression for the current in terms
of a series that is rapidly convergent and each of whose terms is a
simple analytic function. With this setup it is easy to characterize
the dependence of different properties of interest on the current, and
this allows the design and optimization of diverse GRIN PS devices.

@@

The electrostatic potential produced by an infinite array of
charges expressed as a sum in real space of Coulomb terms has ill
convergence properties. The potential can be obtained
using the Ewald summation technique
\cite{ewald1921calculation, belhadj1991molecular-dynamics,
  schmidt1997multipole, grzybowski2000ewald, toukmaji2000efficient,
  brodka2004ewald, campione2012ewald}, which yields
two rapidly converging series, one in real space and another one in reciprocal space.
Nevertheless, as we need the potential and the field to obtain the
current density on the surface of the sample on which  no
real nor image charges lie, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors \cite{nijboer1957calculation, nijboer1958internal,
  de_wette1965internal, watson1981madelung, grindlay1981k}
\notaL{¿De qué se trata esta referencia que pusiste
  aquí: \cite{kratzer2019basics}?}, \notaC{Lo que quiero con este paper 
es resaltar los Conceptos básicos de la cristalografía, 
grupo de puntos cristalográficos, la red recíproca y algunos relaciones de la 
zona de Brillouin.}
then sum over the charges that form the basis
of the 2D {\em crystal} plane, and finally sum over all the
 planes.

@@

In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture GRIN PS structures.
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a silver plate\notaC{ plata.}\notaL{Porqué
vivechna dice silver/copper? De qué era: latón, plata, cobre, una
aleación de cobre y plata? Era un alambre o una placa?}
\notaV{CRISTIAN :  POR FAVOR COLOCAS lo que usaste.}
which together make the anode. The
cathode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the thickness, density and depth
of the resulting pores.

@@

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra at different positions over our
samples using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer in its data collection absolute
reflectance mode, using a rectangular spot size of
$0.7\text{mm}\times2.0\text{mm}$, a slit width of $0.6\text{mm}$ and
a wavelength range from $1400\text{nm}$ to
$300\text{nm}$.\notaL{Vivechna: puedes checar si así se reportan estos parámetros?}
\notaV{CHANGED}
For interpretation of the data we used
the standard formula \cite{stenzel2015physics} for the reflectance of
a three media system:
an air environment  (0), the PS film (1) and the c-Si substrate (2),
\begin{equation}\label{Eq:ECMR}
  R=\left |\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\psi}}{1+r _ {_
        {01}}r _ {_ {12}} e^{2i\psi}}\right |^2
\end{equation}
where $r_{01}$ and $r_{12}$ are the Fresnel reflectance
coefficients of the air/PS and PS/c-Si interfaces \cite{sattler2017silicon}
and $\psi=k_1^\perp d$, where $k_1^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$. The reflectance depends on the
thickness of the film and on the index of refraction $n_1=n_{\text{PS}}$ of the porous
layer, which we relate to the porosity through Bruggeman's
effective medium theory \cite{theiss1997optical},
\begin{equation}\label{Eq:Brugg}
 p\frac{1-\epsilon_1} {1+\epsilon_1} + (1-p)
  \frac{\epsilon_2 - \epsilon_1}
  {\epsilon_2+\epsilon_1}=0,
\end{equation}
where $\epsilon_2=\epsilon_{\text{Si}}$ is the dielectric function of
the c-Si substrate, and
$\epsilon_1=n_{\text{PS}}^2$ is the dielectric function of the PS layer.
We fitted the reflectance spectra using the porosity $p$ and the
thickness $d$ and a scale calibration factor $s$ as fitting
parameters, and thus, we obtained the porosity
$p$ and the etching rate $v=d/t$ for different values of the local
current density $j_\perp$ expected at several positions on different
samples.

@@

\section*{Acknowledgments}
\label{sec:acknowledgments}
WLM acknowledges the support of DGAPA-UNAM under grant
IN111119. \notaL{Cristian debe agradecer a conacyt y faltan
  agradecimientos de Vivechna (quizás incluyendo al icf)}
\notaV{ acknowledges support from CONACyT Basic Sciences project A-S1 30393, 
PRODEP and ICF.}
\bibliographystyle{unsrt}
\bibliography{bibligrin} %Aquí ponen el nombre del archivo .bib
\end{document}
